Demonstration of matching route networks

### 2024-02-01 r/demo.qmd
try geos on intersection road

```{r}
devtools::load_all()
```

```{r}
library(stplanr)
library(sf)
library(rsgeo)
rnet_y = route_network_small["flow"]
rnet_y$id = 1:nrow(rnet_y)
# The target object
rnet_x = rnet_subset(osm_net_example[1], rnet_y)
# Get start and end points for each linestring in rnet_x:
rnet_x_s = lwgeom::st_startpoint(rnet_x)
rnet_x_e = lwgeom::st_endpoint(rnet_x)
plot(rnet_x$geometry, lwd = 9, col = "lightgrey")
plot(rnet_y["flow"], add = TRUE, lwd = 5)
plot(rnet_x_s, add = TRUE, pch = 3)
plot(rnet_x_e, add = TRUE, pch = 3)
```

@@

dist = 10
angle = 5
rnet_merged = stplanr::rnet_merge(rnet_xp, rnet_yp, dist = dist, funs = funs, max_angle_diff = angle, segment_lentgh = 10)

library(tmap)
tmap_mode("plot") # Set to view for interactive mode

>>>>

```{r}
# devtools::load_all()
# remotes::install_dev("rsgeo")
# remotes::install_dev("stplanr")
```

```{r}
library(stplanr)
library(tmap)
library(sf)
library(rsgeo)
rnet_y = route_network_small["flow"]
rnet_y$id = 1:nrow(rnet_y)
# The target object
rnet_x = rnet_subset(osm_net_example[1], rnet_y)
# Get start and end points for each linestring in rnet_x:
rnet_x_s = lwgeom::st_startpoint(rnet_x)
rnet_x_e = lwgeom::st_endpoint(rnet_x)
plot(rnet_x$geometry, lwd = 9, col = "lightgrey")
plot(rnet_y["flow"], add = TRUE, lwd = 5)
plot(rnet_x_s, add = TRUE, pch = 3)
plot(rnet_x_e, add = TRUE, pch = 3)
```

@@

dist = 10
angle = 5
rnet_merged = stplanr::rnet_merge(rnet_xp, rnet_yp, dist = dist,  segment_length = 10, funs = funs, max_angle_diff = angle)

tmap_mode("plot") # Set to view for interactive mode
